A novel distributed nature-inspired algorithm for solving optimization problems

### 2021-09-30 paper.tex
Final Update
Minor stetic update

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

@@

\begin{document}
%
\title{A novel distributed nature-inspired algorithm for solving optimization problems}
% (Biological) Life-Cycle Algorithm: A novel distributed nature-inspired algorithm for solving optimization problems
%
\titlerunning{Life-Cycle Algorithm}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{J. C. Felix-Saul \inst{1} \and
Mario García Valdez\inst{1} \and
Juan J. Merelo Guervós\inst{2}}
%
\authorrunning{Felix-Saul et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Department of Graduate Studies, Tijuana Institute of Technology, Tijuana, Mexico \and
Department of Computer Architecture and Technology, Universidad de Granada, Granada, Spain}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 150--250 words.

Several bio-inspired algorithms use population evolution as analogies of
nature. In this paper, we present an algorithm inspired by the biological
Life-Cycle of animal species, which consists of several stages: birth, growth,
reproduction, and death. As in nature, we intend to execute all these stages in
parallel and asynchronously on a population that evolves constantly. From the
ground up, we designed the algorithm as a cloud-native solution using the cloud
available resources to divide the processing workload among several computers
or running the algorithm as a cloud service. The algorithm works concurrently
and asynchronously on a constantly evolving population, using different
computers (or containers) independently, eliminating waiting times between
processes. This algorithm seeks to imitate the natural life cycle, where new
individuals are born at any moment and mature over time, where they age and
suffer mutations throughout their lives. In reproduction, couples match by
mutual attraction, where they may have offspring. Death can happen to everyone:
from a newborn to an aged adult, where the individual's fitness will impact
their longevity. As a proof-of-concept, we implemented the algorithm with
Docker containers by solving the OneMax problem comparing it with a basic
(sequential) GA algorithm, where it showed favorable and promising results.

\keywords{Distributed Bioinspired Algorithms  \and Genetic Algorithms \and Cloud Computing.}
\end{abstract}

\section{Introduction}

@@

\section{Proposal}
\label{proposal_section}

@@

Experiment 1: The goal of our first OneMax experiment was to make sure our
Life-Cycle algorithm worked as expected, converging on the solution. For this
experiment, we intentionally used delays (on the tenth of a second magnitude)
to follow the Life-Cycle algorithm behavior on the console output. For this
experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
processes (on containers) where we show the summarized results in Table~\ref{tab2}, and
Figure~\ref{fig6} shows their Box and Whisker chart.

@@

Experiment 2: The goal of our second experiment was to confirm the Life-Cycle
algorithm continued working as expected, converging on the solution. For this
experiment, we reduced the time used on delays (now on the thousands of a
second magnitude) to follow the Life-Cycle algorithm behavior. For this
experiment, we only used tournament selection for the reproduction, on the
first configuration running the Life-Cycle on ten processes, versus the second
configuration where we reduced the processes to the minimum basic 5. We show
the summarized results in Table~\ref{tab3}, and Figure~\ref{fig7} shows their Box and Whisker
chart.

@@

Experiment 3: The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table~\ref{tab4},
and Figure~\ref{fig8} shows their Box and Whisker chart.

@@

Experiment 4: The goal of our fourth and last experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we compared the OneMax DEAP
implementation versus the Life-Cycle algorithm, only using tournament selection
for the reproduction, with the Life-Cycle configuration running on the minimum
(five) processes but increasing the (Death) goal approval range to 125. We show
the summarized results in Table~\ref{tab5}, and Figure~\ref{fig9} shows their Box and Whisker
chart.

@@

% Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.

@@

\section*{Acknowledgments}

This paper has been supported in part by projects DeepBio
(TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
%
%
%

% Introducción 
% Contexto: Los algoritmos bioinsirados se utilzan para resolver 
% problemas complejos, pero en ocasiones se requiere de poder
% computo.
% Problemas: La mayoría de los algoritmos bio inspiarados
% no están diseñandos con perspectiva distribuida, paralela y asíncrona. 
% De que hay arquitecturas que tratan esta problematica. 
% Propuesta. 
% Descripción de las secciones del paper.

% Estado del Arte 
% PSO distribuido, GAs, etc.

% Propuesta
%

% Experimental 
% Setup 
% OneMax
% Results

% Conclusiones

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}
%
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{newtxtext}       % 
\usepackage{newtxmath}       % selects Times Roman as basic font

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{document}

\title*{A novel distributed nature-inspired algorithm for solving optimization problems} 
\titlerunning{(Biological) Life-Cycle Algorithm}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario García Valdez, and Juan J. Merelo Guervós}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
\and Juan J. Merelo Guervós \at Universidad de Granada, Granada, Spain \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{Several bio-inspired algorithms use population evolution as
analogies of nature. In this paper, we present an algorithm inspired by the
biological Life-Cycle of animal species, which consists of several stages:
birth, growth, reproduction, and death. As in nature, we intend to execute all
these stages in parallel and asynchronously on a population that evolves
constantly. From the ground up, we designed the algorithm as a cloud-native
solution using the cloud available resources to divide the processing workload
among several computers or running the algorithm as a cloud service. The
algorithm works concurrently and asynchronously on a constantly evolving
population, using different computers (or containers) independently,
eliminating waiting times between processes. This algorithm seeks to imitate
the natural life cycle, where new individuals are born at any moment and mature
over time, where they age and suffer mutations throughout their lives. In
reproduction, couples match by mutual attraction, where they may have
offspring. Death can happen to everyone: from a newborn to an aged adult, where
the individual's fitness will impact their longevity. As a proof-of-concept, we
implemented the algorithm with Docker containers by solving the OneMax problem
comparing it with a basic (sequential) GA algorithm, where it showed favorable
and promising results.}

\abstract{Several bio-inspired algorithms use population evolution as analogies
of nature. In this paper, we present an algorithm inspired by the biological
Life-Cycle of animal species, which consists of several stages: birth, growth,
reproduction, and death. As in nature, we intend to execute all these stages in
parallel and asynchronously on a population that evolves constantly. From the
ground up, we designed the algorithm as a cloud-native solution using the cloud
available resources to divide the processing workload among several computers
or running the algorithm as a cloud service. The algorithm works concurrently
and asynchronously on a constantly evolving population, using different
computers (or containers) independently, eliminating waiting times between
processes. This algorithm seeks to imitate the natural life cycle, where new
individuals are born at any moment and mature over time, where they age and
suffer mutations throughout their lives. In reproduction, couples match by
mutual attraction, where they may have offspring. Death can happen to everyone:
from a newborn to an aged adult, where the individual's fitness will impact
their longevity. As a proof-of-concept, we implemented the algorithm with
Docker containers by solving the OneMax problem comparing it with a basic
(sequential) GA algorithm, where it showed favorable and promising results.}

\section{Introduction}
\label{sec:1}

@@

\section{Proposal}
\label{proposal_section}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head

@@

\subsubsection{Experiment 1}
The goal of our first OneMax experiment was to make sure our
Life-Cycle algorithm worked as expected, converging on the solution. For this
experiment, we intentionally used delays (on the tenth of a second magnitude)
to follow the Life-Cycle algorithm behavior on the console output. For this
experiment, we compared the DEAP algorithm versus the Life-Cycle using ten
processes (on containers) where we show the summarized results in Table~\ref{tab2}, and
Figure~\ref{fig6} shows their Box and Whisker chart.

@@

\subsubsection{Experiment 2}
The goal of our second experiment was to confirm the Life-Cycle
algorithm continued working as expected, converging on the solution. For this
experiment, we reduced the time used on delays (now on the thousands of a
second magnitude) to follow the Life-Cycle algorithm behavior. For this
experiment, we only used tournament selection for the reproduction, on the
first configuration running the Life-Cycle on ten processes, versus the second
configuration where we reduced the processes to the minimum basic 5. We show
the summarized results in Table~\ref{tab3}, and Figure~\ref{fig7} shows their Box and Whisker
chart.

@@

\subsubsection{Experiment 3}
The goal of our third experiment was to follow and study the
behavior of the Life-Cycle algorithm that continued converging on the solution.
For this experiment, we remained using minimal delays (thousands of a second
magnitude). For this experiment, we only used tournament selection for the
reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in Table~\ref{tab4},
and Figure~\ref{fig8} shows their Box and Whisker chart.

@@

\subsubsection{Experiment 4}
The goal of our fourth and last experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we compared the OneMax DEAP
implementation versus the Life-Cycle algorithm, only using tournament selection
for the reproduction, with the Life-Cycle configuration running on the minimum
(five) processes but increasing the (Death) goal approval range to 125. We show
the summarized results in Table~\ref{tab5}, and Figure~\ref{fig9} shows their Box and Whisker
chart.

@@

@@

\begin{acknowledgement}
    This paper has been supported in part by projects DeepBio (TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
\end{acknowledgement}

% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}

\end{document}
